The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.  The resulting limit, if it exists, should then encode some interesting information about your initial set of data.

>>>>

Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.  The resulting limit, if it exists, should then encode some interesting information about your initial set of data.
